Figures and Analysis for 2023 Manuscript

### 2023-11-16 data-raw/Manuscript2023_Workflow.Rmd
Updated with filtered cvt data.

# Writing to file
left_join(my_nca, my_cvt_unique) %>%
  ungroup() %>%
  filter(!is.infinite(AUC_infinity.nca), !is.infinite(AUMC_infinity.nca)) %>%
  distinct() %>%
  mutate(nca_id = row_number(),
         .before = analyte_dtxsid) %>% View("NCA-CvTdb")
  # write_tsv("data-raw/NCA_CvTdb.tsv")
# Note that this will have more numbers because it still includes AUC_infinity == NA

@@

left_join(my_tkstats, my_cvt_unique) %>%
  left_join(prefit_df) %>%
  ungroup() %>%
  distinct() %>%
  mutate(tkstats_id = row_number(), .before = analyte_dtxsid) %>% View("TKstats-CvTdb")
  # write_tsv("data-raw/tkstats_CvTdb.tsv")

>>>>

# Writing to file
left_join(my_nca, my_cvt_unique) %>%
  ungroup() %>%
  filter(!is.infinite(AUC_infinity.nca), !is.infinite(AUMC_infinity.nca)) %>%
  distinct() %>%
  mutate(nca_id = row_number(),
         .before = analyte_dtxsid) %>%
  # View("NCA-CvTdb")
  write_tsv("data-raw/NCA_CvTdb.tsv")
# Note that this will have more numbers because it still includes AUC_infinity == NA

@@

left_join(my_tkstats, my_cvt_unique) %>%
  left_join(prefit_df) %>%
  ungroup() %>%
  distinct() %>%
  mutate(tkstats_id = row_number(), .before = analyte_dtxsid) %>%
  # View("TKstats-CvTdb")
  write_tsv("data-raw/tkstats_CvTdb.tsv")
